### 2025-09-23 paper/sec/authoring-workflow.tex
Just summarise system prompt; refer to appendix for full.

\begin{itemize}
\item \textbf{Input structure:} summarises the imported datasets, modules, auxililiary definitions in scope in
the current file, the current Fluid representation of the target paragraph with \kw{[REPLACE …]} tag
indicating the text fragment to replace, plus the full text for the paragraph.
\item \textbf{Task description:} description of the LLM task, namely to identify the placeholder, generate a
Fluid expression that produces the target string using supplied dataset and definitions in scope.
\item \textbf{Output constraints:} specify that the LLM should return a syntactically valid Fluid expression,
with no extraneous content (such as comments).
\end{itemize}

\begin{figure}[h]
    \centering
    \begin{tcolorbox}[colback=gray!10, colframe=gray!50, boxrule=0.5pt, arc=2pt,
        left=6pt, right=6pt, top=4pt, bottom=4pt]
        \VerbatimInput[fontsize=\small, formatcom=\normalfont]{../system-prompt/interpretation-agent/system-prompt.txt}
    \end{tcolorbox}
    \vspace{-0.5em}
    \caption{System Prompt defined for the Authoring Assistant}
    \label{fig:system-prompt}
\end{figure}

>>>>

\begin{itemize}
\item \textbf{Input structure:} summarises the imported datasets, modules, auxililiary definitions in scope in
the current file, the current Fluid representation of the target paragraph with \kw{[REPLACE …]} tag
indicating the text fragment to replace, plus the full text for the paragraph.
\item \textbf{Task description:} description of the LLM task, namely to identify \kw{[REPLACE …]} placeholder
and generate Fluid expression that produces target string using supplied dataset and definitions in scope.
\item \textbf{Output constraints:} specify that the LLM should return a syntactically valid Fluid expression,
with no extraneous content (such as comments).
\end{itemize}
